

```{r options, echo=FALSE}
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(echo = FALSE)
```

```{r load-data, results="hide"}
b.df <- read.csv("../data/badge.csv")
```

According to the figure below, the badge size increases with wing
length, however it seems to have some effect of the sex too.

```{r plot-data, results="hide"}
png(file="../work/badge_wing-length.png", width=6, height=6, units="in",
		res=600)
opar <- par(mar=c(5,5,1,1)+0.1)
plot(badge.size ~ wing.length, b.df, type="n", xlab="wing length [mm]",
		 ylab=expression(paste("badge size [", mm^2, "]", sep="")))
points(badge.size ~ wing.length, b.df, subset = sex == "female")
points(badge.size ~ wing.length, b.df, subset = sex == "male", pch=16)
legend("topleft", legend=levels(b.df$sex), pch=c(1,16), bty="n",
			 title="sex")
par(opar)
dev.off()
```

![The relation between wing length and badge size, for males and
females](work/badge_wing-length.png)

```{r analyse-data, results="hide"}
z <- lm(badge.size ~ wing.length * sex, b.df)
z1 <- update(z, .~. - wing.length:sex)
a <- anova(z1)
```

The statistical analysis fully supports the above observations. Badge
size increases with wing length (*F*~`r paste(a$Df[c(1,3)], collapse=",")`~ = 
`r round(a$"F value"[1], 2)`, *p* = `r round(a$"Pr(>F)"[1], 3)`) and
males have larger sized badges (*F*~`r paste(a$Df[c(2,3)], collapse=",")`~ = 
`r round(a$"F value"[2], 2)`, *p* = `r round(a$"Pr(>F)"[2], 3)`).
